Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-07-26 Draft.tex
Remove commented packages
Use graphicspath
Add directories for graphicspath

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{amsfonts}
% \usepackage{parskip}
\usepackage{natbib}
% \usepackage{color}
% \usepackage[dvipsnames]{xcolor}
\usepackage[margin=1cm]{caption}
\usepackage{adjustbox}
% \usepackage[toc,page]{appendix}
% \usepackage{enumitem}
% \usepackage{multirow} 
\usepackage{setspace} % for \doublespacing
% \usepackage{url}
\usepackage{xr} % for cross referencing to supplement
% \usepackage{lineno}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Oral Prelim/AMRO_JABES"} % Source file: Oral Prelim/TTDD_Demo.R
\caption{\label{fig:schematic} 
Illustration of fitting mixture exponential (left) and mixture gamma (right) time-to-detection distributions (TTDDs) to interval-censored removal-sampled observations (center).
The mixture TTDD consists of a continuous TTDD (thick line) plus a mixture component of first-interval detections (light gray rectangle), constituting $\gamma$ and $1-\gamma$ proportions of the population, respectively.
We estimate $\pdet$ as the proportion of the TTDD before the end of the observation period $C$, leaving an estimated proportion $1-\pdet$ undetected.
}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/mixture_fig"} % Source file: Sims/SimZero/Outputs_Code_zero.R
\caption{
Comparisons of mixture and non-mixture TTDDs.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 90\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}: Data simulated from non-mixture (upper) or mixture (lower) TTDDs.  \textit{Columns}:  Data simulated from nonpeaked (left), exponential (center), or peaked (right) TTDDs.  Each inference model was fit only to datasets from the same TTDD family (e.g. lognormal to lognormal).
}
\label{fig:mixture_fig} 
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/Posteriors_Families_draft"} % Source file: Sims/SimZero/RepresentativePosteriors.R
\caption{\label{fig:sim2typical} 
Representative examples of posterior distributions for $\pdet$ (left panel) and survey-level log-scale abundance (right panel).
Data are simulated from nonpeaked gamma (left column), exponential (center), and peaked gamma (right) mixture TTDDs.
True detection probabilities vary by row and are shown for comparison (dashed vertical line).
Inference models are either exponential mixture (light gray) or gamma mixture (dark gray) TTDDs.
}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{"Sims/SimZero/family_fig"} % Source file: Sims/SimZero/Outputs_Code_zero.R
\caption{
Comparisons of TTDDs across families.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 90\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}:  Data simulated from mixture exponential, gamma, lognormal, or Weibull TTDDs.  \textit{Columns}: Data simulated from nonpeaked or exponential (left) or peaked (right) TTDDs.  All data and inference models used mixture TTDDs.
}
\label{fig:family_fig}
\end{figure}

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.95\textwidth]{OVEN/oven_sum/OVEN_Posteriors} % Source file: OVEN/Compile.R
\caption{\label{ovenposteriors} Posterior medians (black dots) with 50\% (wider line) and 95\% (narrowerline) credible intervals for the mixing parameter ($\gamma$), shape parameter ($\alpha$) as well as abundance (A) and detection (D) fixed effects and random effect standard deviations.
Posteriors are also available for the overall probability of detection and the abundance across all sites.}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[margin=1cm]{caption}
\usepackage{adjustbox}
\usepackage{setspace} % for \doublespacing
\usepackage{xr} % for cross referencing to supplement

\graphicspath{{"Oral Prelim/"}{Sims/SimZero/}{OVEN/oven_sum/}}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{AMRO_JABES} % Source file: Oral Prelim/TTDD_Demo.R
\caption{\label{fig:schematic} 
Illustration of fitting mixture exponential (left) and mixture gamma (right) time-to-detection distributions (TTDDs) to interval-censored removal-sampled observations (center).
The mixture TTDD consists of a continuous TTDD (thick line) plus a mixture component of first-interval detections (light gray rectangle), constituting $\gamma$ and $1-\gamma$ proportions of the population, respectively.
We estimate $\pdet$ as the proportion of the TTDD before the end of the observation period $C$, leaving an estimated proportion $1-\pdet$ undetected.
}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{mixture_fig} % Source file: Sims/SimZero/Outputs_Code_zero.R
\caption{
Comparisons of mixture and non-mixture TTDDs.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 90\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}: Data simulated from non-mixture (upper) or mixture (lower) TTDDs.  \textit{Columns}:  Data simulated from nonpeaked (left), exponential (center), or peaked (right) TTDDs.  Each inference model was fit only to datasets from the same TTDD family (e.g. lognormal to lognormal).
}
\label{fig:mixture_fig} 
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{Posteriors_Families_draft} % Source file: Sims/SimZero/RepresentativePosteriors.R
\caption{\label{fig:sim2typical} 
Representative examples of posterior distributions for $\pdet$ (left panel) and survey-level log-scale abundance (right panel).
Data are simulated from nonpeaked gamma (left column), exponential (center), and peaked gamma (right) mixture TTDDs.
True detection probabilities vary by row and are shown for comparison (dashed vertical line).
Inference models are either exponential mixture (light gray) or gamma mixture (dark gray) TTDDs.
}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\textwidth]{family_fig} % Source file: Sims/SimZero/Outputs_Code_zero.R
\caption{
Comparisons of TTDDs across families.  \textit{Left}: Average posterior median detection probabilities across 100 replicate simulations.  Dashed lines show unbiased estimation.   \textit{Right}: Coverage of 90\% credible intervals across 100 replicate simulations.  Dashed lines depict a 95\% range of observed coverage that is consistent with nominal coverage.  \textit{Rows}:  Data simulated from mixture exponential, gamma, lognormal, or Weibull TTDDs.  \textit{Columns}: Data simulated from nonpeaked or exponential (left) or peaked (right) TTDDs.  All data and inference models used mixture TTDDs.
}
\label{fig:family_fig}
\end{figure}

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.95\textwidth]{OVEN_Posteriors} % Source file: OVEN/Compile.R
\caption{\label{ovenposteriors} Posterior medians (black dots) with 50\% (wider line) and 95\% (narrowerline) credible intervals for the mixing parameter ($\gamma$), shape parameter ($\alpha$) as well as abundance (A) and detection (D) fixed effects and random effect standard deviations.
Posteriors are also available for the overall probability of detection and the abundance across all sites.}
\end{figure}
